---
title: "R Notebook"
output: html_notebook
---
CTG <- read.csv("C:/Users/17875/Downloads/CTG.csv", header = TRUE)
str(CTG)


#Install Packages
```{r}
library(keras)
#install_keras()
library(tidyverse)
```
#CTG <- read.csv("C:/Users/17875/Downloads/CTG.csv", header = TRUE)
#Read the data
```{r}
Nndata <- read.csv(file.choose(), header = T) #CTG <- read.csv("C:/Users/17875/Downloads/CTG.csv", header = TRUE)
str(Nndata)
```

```{r}
normalizer <- function(df, columnName){
  mt_colum <- colnames(df[,columnName])
  
 
  for (x in mt_colum) {
    tem <- c()
    
    i <- 1
    
    for(y in df[,x]){
    
    tem[i] <- (y - min(df[,x])) / (max(df[,x]) - min(df[,x]))
     i <- i + 1
    
    }
    df[,x] <- tem
  }
  
  df <- as.data.frame(df)
  
  return(df)
}
data2 <- normalizer(Nndata, c(1:21))
```

```{r}
data
```

```{r}
data$NSP <- as.factor(data$NSP)
data$Tendency <- as.factor(data$Tendency)
```


```{r}
dataP1 <- ggplot(data = data, mapping = aes(x = ASTV, y = ALTV, color = NSP)) + 
  geom_point() + theme(legend.position = "top")
dataP1
```

```{r}
dataP2 <- ggplot(data = data, mapping = aes(x = Nmax, y = Nzeros, color = Tendency)) + 
  geom_point()
dataP2
```


```{r}
dataP3 <- ggplot(data = data, mapping = aes(x = Min, y = Max, color = NSP)) + 
  geom_point()
dataP3
```

```{r}
dataP4 <- ggplot(data = data, mapping = aes(x = LB, y = FM, color = NSP)) + 
  geom_point()
dataP4
```


```{r}
data2$class <- Nndata$NSP
```

```{r}
colnames(data2) <- colnames(data)
```

```{r}
data2
```


#Change to Matrix
```{r}
# data <- as.matrix(data)
# dimnames(data) <- NULL
# ```
# 
# #Normalize
# ```{r}
# data[,1:21] <- normalize(data[,1:21])
# data[,22] <- as.factor(data[,22])-1
# summary(data)


```


#Data Partition
```{r}
set.seed(222)
indctg <- sample(2, nrow(data2), replace = TRUE, prob = c(0.7, 0.3))
training <- data2[indctg==1,]
testing <- data2[indctg==2,]
```

```{r}
data2
```

#Neural Network Model
```{r}
library(neuralnet)
set.seed(333)
n <- neuralnet(NSP ~LB+AC+FM+UC +DL+DS+DP+ASTV+MSTV+ALTV+MLTV+Width+
                 Min+Max+Nmax+Nzeros+Mode+Mean+Median+Variance+Tendency,
               data = training,
               hidden = 1, #fist I do with hidden = 1 and was simple now with 5
               err.fct = "sse",
               linear.output = FALSE)
plot(n)
```

#Prediction
```{r}
output <- compute(n, training[,-22])
head(output$net.result)
head(training[1,])
```


```{r}
attributes(n)
```
```{r}
n$data
```

#Node Output Calculation with sigmoid Activation Function
```{r}
# in4 <-  0.0455+(0.82344*0.7586207)+(1.35186*0.8103448)+(-0.87435*0.6666667)
# in4
# out4 <- 1/(1+exp(-in4))
# out4
# in5 <- -7.06125+(8.5741*out4)
# in5
# out5 <- 1/(1+exp(-in5))
# out5
```

Confusion MAtrix and Misclassification Error - trainig data
```{r}
output <- compute(n, training[,-22])
p1 <- output$net.result
pred1 <- ifelse(p1>0.5, 1, 0)
tab1 <- table(pred1, training$NSP)
tab1
1-sum(diag(tab1))/sum(tab1) #accuracy -1 is MIsclassification that is 0.2237999
sum(diag(tab1))/sum(tab1)
```

```{r}
Nn_dfrP1 <- tab1
Nn_dfrP1 <- as.data.frame(Nn_dfrP1)
Nn_dfrP1 <- mutate(Nn_dfrP1, tab = "NnP1")
Nn_dfrP1 
write.csv(Nn_dfrP1, "Nn_dfrP1.csv")
```



Confusion MAtrix and Misclassification Error - testing data
```{r}
output <- compute(n, testing[,-22])
p2 <- output$net.result
pred2 <- ifelse(p2>0.5, 1, 0)
tab2 <- table(pred2, testing$NSP)
tab2
1-sum(diag(tab2))/sum(tab2) #accuracy -1 is MIsclassification that is 0.2163833
sum(diag(tab2))/sum(tab2)
```

```{r}
Nn_dfrP2 <- tab2
Nn_dfrP2 <- as.data.frame(Nn_dfrP2)
Nn_dfrP2 <- mutate(Nn_dfrP2, tab = "NnP2")
Nn_dfrP2
write.csv(Nn_dfrP2, "Nn_dfrP2.csv")
```


#More Neurons in Hidden Layer
```{r}
library(neuralnet)
set.seed(333)
n5 <- neuralnet(NSP ~LB+AC+FM+UC +DL+DS+DP+ASTV+MSTV+ALTV+MLTV+Width+
                 Min+Max+Nmax+Nzeros+Mode+Mean+Median+Variance+Tendency,
               data = training,
               hidden = 5, #fist I do with hidden = 1 and was simple now with 5
               err.fct = "sse",
               linear.output = FALSE)
plot(n5)
```

#Prediction
```{r}
output5 <- compute(n5, training[,-22])
head(output5$net.result)
head(training[1,])
```



Confusion MAtrix and Misclassification Error - trainig data
```{r}
output5 <- compute(n5, training[,-22])
p1_5 <- output5$net.result
pred1_5 <- ifelse(p1_5>0.5, 1, 0)
tab1_5 <- table(pred1_5, training$NSP)
tab1_5
1-sum(diag(tab1_5))/sum(tab1_5) #accuracy -1 is MIsclassification that is 0.2237999
sum(diag(tab1_5))/sum(tab1_5)
```


```{r}
Nn5_dfrP1 <- tab1_5
Nn5_dfrP1 <- as.data.frame(Nn5_dfrP1)
Nn5_dfrP1 <- mutate(Nn5_dfrP1, tab = "Nn5P1")
Nn5_dfrP1
write.csv(Nn5_dfrP1, "Nn5_dfrP1.csv")
```



Confusion MAtrix and Misclassification Error - testing data
```{r}
output5 <- compute(n5, testing[,-22])
p2_5 <- output5$net.result
pred2_5 <- ifelse(p2_5>0.5, 1, 0)
tab2_5 <- table(pred2_5, testing$NSP)
tab2_5
1-sum(diag(tab2_5))/sum(tab2_5) #accuracy -1 is MIsclassification that is 0.2163833
sum(diag(tab2_5))/sum(tab2_5)
```


```{r}
Nn5_dfrP2 <- tab2_5
Nn5_dfrP2 <- as.data.frame(Nn5_dfrP2)
Nn5_dfrP2 <- mutate(Nn5_dfrP2, tab = "Nn5P2")
Nn5_dfrP2
write.csv(Nn5_dfrP2, "Nn5_dfrP2.csv")
```

#Neural Network with two Hidden Layers
```{r}
library(neuralnet)
set.seed(333)
nC <- neuralnet(NSP ~LB+AC+FM+UC +DL+DS+DP+ASTV+MSTV+ALTV+MLTV+Width+
                 Min+Max+Nmax+Nzeros+Mode+Mean+Median+Variance+Tendency,
               data = training,
               hidden = c(2,1), #fist I do with hidden = 1 and was simple now with 5
               err.fct = "sse",
               linear.output = FALSE)
plot(nC)
```

#Prediction
```{r}
outputC <- compute(nC, training[,-22])
head(outputC$net.result)
head(training[1,])
```



Confusion MAtrix and Misclassification Error - trainig data
```{r}
outputC <- compute(nC, training[,-22])
p1C <- outputC$net.result
pred1C <- ifelse(p1>0.5, 1, 0)
tab1C <- table(pred1C, training$NSP)
tab1C
1-sum(diag(tab1C))/sum(tab1C) #accuracy -1 is MIsclassification that is 0.2237999
sum(diag(tab1C))/sum(tab1C)
```


```{r}
NnC_dfrP1 <- tab1C
NnC_dfrP1 <- as.data.frame(NnC_dfrP1)
NnC_dfrP1 <- mutate(NnC_dfrP1, tab = "NnC2_1P1")
NnC_dfrP1
write.csv(NnC_dfrP1, "NnC_dfrP1.csv")
```



Confusion MAtrix and Misclassification Error - testing data
```{r}
outputC <- compute(nC, testing[,-22])
p2C <- outputC$net.result
pred2C <- ifelse(p2>0.5, 1, 0)
tab2C <- table(pred2C, testing$NSP)
tab2C
1-sum(diag(tab2C))/sum(tab2C) #accuracy -1 is MIsclassification that is 0.2163833
sum(diag(tab2C))/sum(tab2C)
```

```{r}

```



```{r}
NnC_dfrP1 <- tab1C
NnC_dfrP1 <- as.data.frame(NnC_dfrP1)
NnC_dfrP1 <- mutate(NnC_dfrP1, tab = "NnC2_1P1")
NnC_dfrP1
write.csv(NnC_dfrP1, "NnC_dfrP1.csv")
```


#Neural Network Repeat Calculations
```{r}
library(neuralnet)
set.seed(333)
n5R <- neuralnet(NSP ~LB+AC+FM+UC +DL+DS+DP+ASTV+MSTV+ALTV+MLTV+Width+
                 Min+Max+Nmax+Nzeros+Mode+Mean+Median+Variance+Tendency,
               data = training,
               hidden = 5, #fist I do with hidden = 1 and was simple now with 5
               err.fct = "sse",
               linear.output = FALSE,
               lifesign = "full",
               rep = 5,
               algorithm = "rprop+", #default Algorithm RPROP+: Resilient Backpropagation with Weight Backtacking
               stepmax = 100000)
plot(n5R, rep=1)
```

#Prediction
```{r}
output5R <- compute(n5R, training[,-22])
head(output5R$net.result)
head(training[1,])
```



Confusion MAtrix and Misclassification Error - trainig data
```{r}
output5R <- compute(n5R, training[,-22])
p15R <- output5R$net.result
pred15R <- ifelse(p1>0.5, 1, 0)
tab15R <- table(pred15R, training$NSP)
tab15R
1-sum(diag(tab15R))/sum(tab15R) #accuracy -1 is MIsclassification that is 0.2237999
sum(diag(tab15R))/sum(tab15R)
```


```{r}
Nn5R_dfrP1 <- tab15R
Nn5R_dfrP1 <- as.data.frame(Nn5R_dfrP1)
Nn5R_dfrP1 <- mutate(Nn5R_dfrP1, tab = "Nn5R_P1")
Nn5R_dfrP1
write.csv(Nn5R_dfrP1, "Nn5R_dfrP1.csv")
```


Confusion MAtrix and Misclassification Error - testing data
```{r}
output5R <- compute(n5R, testing[,-22])
p25R <- output5R$net.result
pred25R <- ifelse(p2>0.5, 1, 0)
tab25R <- table(pred25R, testing$NSP)
tab25R
1-sum(diag(tab25R))/sum(tab25R) #accuracy -1 is MIsclassification that is 0.2163833
sum(diag(tab25R))/sum(tab25R)
```