---
title: "R Support Vector Machine"
output: html_notebook
---

#Classification using Support Vector MAchine
```{r}
CTG <- read.csv("C:/Users/17875/Downloads/CTG.csv", header = TRUE)
str(CTG)
```

```{r}
CTG$NSP <- as.factor(CTG$NSP)
str(CTG)
```


```{r}
library(ggplot2)
library(tidyverse)
```


```{r}
qplot(Max, Min , data = CTG,
      color = NSP )
```

```{r}
qplot(ASTV , ALTV , data = CTG,
      color = NSP)
```


#Support Vector Machine

```{r}
library(e1071)
```

```{r}
mymodel <- svm(NSP~ Max + Min + ASTV + ALTV, data = CTG)
summary(mymodel)
```

```{r}
plot(mymodel, data = CTG,
     ALTV ~ ASTV,
     slice = list(Min = 3, Max = 4))

```

#Confusion Matrix & Misclassification Error
```{r}
predic <- predict(mymodel, CTG)
tab <- table(Predicted= predic,Actual = CTG$NSP)
tab
```
Misclassification =  0.09548448 / Acuracy= 0.9045155 
```{r}
1-sum(diag(tab))/sum(tab) 
```
#Linear Classification
```{r}
mymodel <- svm(NSP ~ Max + Min + ASTV + ALTV, data = CTG,
               kernel = "linear")
summary(mymodel)
```
```{r}
plot(mymodel, data = CTG,
     ASTV ~ ALTV,
    slice = list(Min = 3, Max = 4))

```
#Confusion Matrix & Misclassification Error
```{r}
predic <- predict(mymodel, CTG)
tab <- table(Predicted= predic,Actual = CTG$NSP)
tab
```


Misclassification = 0.09548448 / Acuracy = 0.9045155
```{r}
1-sum(diag(tab))/sum(tab)
```

#Linear Polinomial
```{r}
mymodel <- svm(NSP ~ Max + Min + ASTV + ALTV, data = CTG, 
               kernel = "polynomial")
summary(mymodel)
```
```{r}
plot(mymodel, data = CTG,
      ASTV ~ ALTV,
     slice = list(Min = 3, Max = 4)
     )
```
#Confusion Matrix & Misclassification Error
```{r}
predic <- predict(mymodel, CTG)
tab <- table(Predicted= predic,Actual = CTG$NSP)
tab
```


Misclassification =0.1321731 / Acuracy = 0.8678269
```{r}
sum(diag(tab))/sum(tab)
```




#Linear Sigmoid
```{r}
mymodel <- svm(NSP~Max + Min + ASTV + ALTV, data = CTG,
               kernel = "sigmoid")
summary(mymodel)
```
```{r}
plot(mymodel, data = CTG,
     ASTV~ALTV,
     slice = list(Min = 3, Max = 4))
```
#Confusion Matrix & Misclassification Error
```{r}
predic <- predict(mymodel, CTG)
tab <- table(Predicted= predic,Actual = CTG$NSP)
tab
```


Misclassification = 0.2685795 / Acuracy = 0.7314205
```{r}
sum(diag(tab))/sum(tab)
```

#Tuning Hipper parameter optimal classification
```{r}
set.seed(123)
tmodel <- tune(svm, NSP~ Max + Min + ASTV + ALTV, data = CTG,
     ranges = list(epsilon = seq(0,1,0.1), cost = 2^(2:7)))
plot(tmodel)
```
```{r}
summary(tmodel)
```

#Best Model
```{r}
mymodel <- tmodel$best.model
summary(mymodel)
```
#Plot
```{r}
plot(mymodel, data = CTG,
     ASTV ~ ALTV,
     slice = list(Max = 3, Min = 4)
     )
```

#Confusion Matrix & Misclassification Error
```{r}
predic <- predict(mymodel, CTG)
tab <- table(Predicted= predic,Actual = CTG$NSP)
tab
```


Misclassification = 0.09548448 / Acuracy = 0.9045155
```{r}
sum(diag(tab))/sum(tab)
```


```{r}
attributes(tmodel)
```

```{r}
tmodel$performances
```

```{r}
tune_tmodelPerformance <- as.table
```

