---
title: "Random Forest"
output: html_notebook
---

```{r}
library(tidyverse)
```


#Random Forest

#Read Data
```{r}
CTG <- read.csv("C:/Users/17875/Downloads/CTG.csv", header = TRUE)
str(CTG)
CTG$NSP <- as.factor(CTG$NSP)
table(CTG$NSP)
```


# Data Partition
```{r}
set.seed(123)
ind <- sample(2, nrow(CTG), replace = TRUE, prob = c(0.7, 0.3))
train <- CTG[ind==1,]
test <- CTG[ind==2,]
```


#Random Forest
```{r}
library(randomForest)
set.seed(222)
rf <- randomForest(NSP~., data = train)
rf
```
 Number of trees: 500 #<-- ntree
No. of variables tried at each split: 4  <--mtry
```{r}
attributes(rf)
```

```{r}
rf$confusion
```

#Prediction and Confusion Matrix --- train data
```{r}
library(caret)
p1 <- predict(rf, train)
head(p1)
head(train$NSP)
```

```{r}
confusionMatrix(p1, train$NSP)
```

#Prediction with test Data
```{r}
p2 <- predict(rf, test)
confusionMatrix(p2, test$NSP)
```

#Error Rate of Raondom forest Model
```{r}
plot(rf)
```

#Tune mtry
```{r}
t <- tuneRF(train[,-22], train[,22],
       stepFactor = .5, 
       plot = TRUE,
       ntreeTry = 300,
       trace = TRUE,
       improve = 0.05)
t
```

#Ramdon Forest Model
```{r}
set.seed(222)
rf <- randomForest(NSP~., data = train,
                   ntree =300,
                   mtry = 8,
                   importance = TRUE,
                   proximity = TRUE)
rf
```

#No. Nodes for the Trees
```{r}
hist(treesize(rf),
     main = "No. Nodes for the Trees",
     col = "green")
```

#Variable  Importance
```{r}
varImpPlot(rf,
           sort = T,
           n.var = 10,
           main = "Top 10 Variable  Importance")
importance(rf)
varUsed(rf)
```

#Partial Defendence Plot
```{r}
partialPlot(rf, train, ASTV, "2")
```

#Extract single tree
```{r}

getTree(rf, 1, labelVar = TRUE)
```

#Multi-dimensional Scaling Plot of Proximity Matrix
```{r}
MDSplot(rf, train$NSP)
```

Neural Network
Deep Learning Neural Network
Random Forest
SVM
AutoML model