---
title: "R Support Vector Machine"
output: html_notebook
---

#Classification using Support Vector MAchine
```{r}
CTG <- read.csv("C:/Users/17875/Downloads/CTG.csv", header = TRUE)
str(CTG)
```

```{r}
CTG$NSP <- as.factor(CTG$NSP)
str(CTG)
```


```{r}
library(ggplot2)
```


```{r}
qplot(Max, Min , data = CTG,
      color = NSP )
```

```{r}
qplot(ASTV , ALTV , data = CTG,
      color = NSP)
```


#Support Vector Machine

```{r}
library(e1071)
```

```{r}
mymodel <- svm(NSP~ Max + Min + ASTV + ALTV, data = CTG)
summary(mymodel)
```

```{r}
plot(mymodel, data = CTG,
     ALTV ~ ASTV,
     slice = list(Min = 3, Max = 4))

```

#Confusion Matrix & Misclassification Error
```{r}
predicR <- predict(mymodel, CTG)
tabR <- table(Predicted= predicR,Actual = CTG$NSP)
tabR
```

```{r}
svmp1_df <- tabR
svmp1_df <- as.data.frame(svmp1_df)
svmp1_df <- mutate(svmp1_df, tab = "svmp1_df")
svmp1_df
write.csv(svmp1_df, "svmp1_Radial_df.csv")
```


Misclassification =  0.121825 / Acuracy= 0.878175 
```{r}
sum(diag(tabR))/sum(tabR) 
```
#Linear Classification
```{r}
mymodelL <- svm(NSP ~ Max + Min + ASTV + ALTV, data = CTG,
               kernel = "linear")
summary(mymodelL)
```
```{r}
plot(mymodelL, data = CTG,
     ASTV ~ ALTV,
    slice = list(Min = 3, Max = 4))

```
#Confusion Matrix & Misclassification Error
```{r}
predicL <- predict(mymodelL, CTG)
tabL <- table(Predicted= predicL,Actual = CTG$NSP)
tabL
```


Misclassification = 0.187206 / Acuracy = 0.812794
```{r}
sum(diag(tabL))/sum(tabL)
```


```{r}
svmpL_df <- tabL
svmpL_df <- as.data.frame(svmpL_df)
svmpL_df <- mutate(svmpL_df, tab = "svmpL_df")
svmpL_df
write.csv(svmpL_df, "svmp_Lineal_df.csv")
```




#Linear Polinomial
```{r}
mymodelP <- svm(NSP ~ Max + Min + ASTV + ALTV, data = CTG, 
               kernel = "polynomial")
summary(mymodelP)
```

```{r}
plot(mymodelP, data = CTG,
      ASTV ~ ALTV,
     slice = list(Min = 3, Max = 4)
     )
```
#Confusion Matrix & Misclassification Error
```{r}
predicP <- predict(mymodelP, CTG)
tabP <- table(Predicted= predicP,Actual = CTG$NSP)
tabP
```


Misclassification =0.1321731 / Acuracy = 0.8678269
```{r}
1-sum(diag(tabP))/sum(tabP)
```

```{r}
svmpP_df <- tabP
svmpP_df <- as.data.frame(svmpP_df)
svmpP_df <- mutate(svmpP_df, tab = "svmP_df")
svmpP_df
write.csv(svmpP_df, "svmp_Polinomial_df.csv")
```



#Linear Sigmoid
```{r}
mymodel_S <- svm(NSP~Max + Min + ASTV + ALTV, data = CTG,
               kernel = "sigmoid")
summary(mymodel_S)
```

```{r}
plot(mymodel_S, data = CTG,
     ASTV~ALTV,
     slice = list(Min = 3, Max = 4))
```
#Confusion Matrix & Misclassification Error
```{r}
predicS <- predict(mymodel_S, CTG)
tabS <- table(Predicted= predicS,Actual = CTG$NSP)
tabS
```

```{r}
svmpSigm_df <- tabS
svmpSigm_df <- as.data.frame(svmpSigm_df)
svmpSigm_df <- mutate(svmpSigm_df, tab = "svmpSigm_df")
svmpSigm_df
write.csv(svmpSigm_df, "svmp_Sigmod_df.csv")
```


Misclassification = 0.2685795 / Acuracy = 0.7314205
```{r}
sum(diag(tabS))/sum(tabS)
```

#Tuning Hipper parameter optimal classification
```{r}
set.seed(123)
tmodel <- tune(svm, NSP~ Max + Min + ASTV + ALTV, data = CTG,
     ranges = list(epsilon = seq(0,1,0.1), cost = 2^(2:7)))
plot(tmodel)
```
```{r}
performance_df <- tmodel$performances
performance_df
```


```{r}
svmpPerfomance_df <- performance_df
svmpPerfomance_df <- as.data.frame(svmpPerfomance_df)

svmpPerfomance_df
write.csv(svmpPerfomance_df, "svmpPerfomance_df.csv")
```



#Best Model
```{r}
mymodel <- tmodel$best.model
summary(mymodel)
```
#Plot
```{r}
plot(mymodel, data = CTG,
     ALTV ~ ASTV,
     slice = list(Max = 3, Min = 4)
     )
```

#Confusion Matrix & Misclassification Error
```{r}
predic <- predict(mymodel, CTG)
tab <- table(Predicted= predic,Actual = CTG$NSP)
tab
```


```{r}
dfmymodelsv <- as.data.frame(mymodel$sv)
dfmymodelsv
```






```{r}

toSVMResulModel <- cbind(mymodel$SV) mymodel$coefs
```



```{r}
svmpBest_df <- tab
svmpBest_df <- as.data.frame(svmpBest_df)
svmpBest_df <- mutate(svmpBest_df, tab = "svmpBest_df")
svmpBest_df
write.csv(svmpBest_df, "svmpBest_df.csv")
```


Misclassification = 0.09548448 / Acuracy = 0.9045155
```{r}
sum(diag(tab))/sum(tab)
```



```{r}
totalSVM <- rbind(svmp1_df,svmpL_df,svmpP_df,svmpSigm_df,svmpBest_df)
totalSVM
write.csv(totalSVM, "svmTotal_df.csv")
```

```{r}
totalSVM$tab <- as.factor(totalSVM$tab)
totalSVM
```

```{r}
ggplot(totalSVM, mapping = aes(Freq, , fill = Predicted)) + geom_histogram()
```
svmpPerfomance_df

```{r}
ggplot(svmpPerfomance_df, aes())
```

